---
title: "De-blinding and cleaning the data collection sheet"
output: 
  workflowr::wflow_html:
    code_folding: hide 
editor_options:
  chunk_output_type: console
---



## De-blinding the raw data collection sheet

All steps of the experiment were run blind to pheromone treatment. For maximum security, there were two levels of blinding: 

- A colleague re-labelled the 12 vials containing the pheromone solutions with a number in the range 1-12, so that we were unaware which vial contained which pheromone when running the experiment and recording the videos.
- Each video shows a tray of 12 Petri dishes containing bees, plus a piece of paper coated with 1 of the 12 pheromone solutions. The Petri dishes containing treatments 1-12 were rotated haphazardly between trays. So for example, treatment 1 might be in the top left corner, the middle, or the bottom-right corner of the tray. Therefore, the person recording the videos did not know which Petri dish contained which treatment number (as well as not knowing which treatments were represented by each number). They were also unaware which hive the bees were obtained from

In the following code chunks, we use the information in the file `data/blind_codes.csv` to create an unblinded dataset from the input data, i.e. `data/blinded_behaviour_data.csv`.

The output file created by this script is called `data/unblinded_behaviour_data.csv` -- this is the file that should be used for running new analyses, checking our conclusions, or including our data in a meta-analysis.


```{r message=FALSE, warning=FALSE}
library(tidyverse)

# Load up the blind codes, to determine the treatment and hive for each Petri dish
blind_codes_full <- read_csv("data/blind_codes.csv")

blind_codes <- blind_codes_full %>%
  filter(tray == 1) %>%
  select(treatment, treat_num)

# Here are the treatments, ranked roughly from least to most like a queen bee
treatment_levels <- 
  # two "controls"
  c("Solvent control", "10-HDA (worker control)", 
    
     # 4 individual queen-type chemicals
    "HOB", "HVA", "9-HDA", "9-ODA",   
    
    # 6 pairwise combinations of two of the queen-type chemicals
    "HOB and HVA",                                
    "9-HDA and HOB", "9-HDA and HVA",
    "9-ODA and HOB", "9-ODA and HVA", "9-ODA and 9-HDA")


unblinded_data <- read.csv("data/blinded_behaviour_data.csv", 
                           stringsAsFactors = FALSE) %>%
  as_tibble() %>%
  filter(!is.na(tray)) %>%
  
  # convert to "time since the start of recording, in seconds"
  mutate(split_start = map(strsplit(start_touch, split = ":"), as.numeric), 
         split_end   = map(strsplit(end_touch, split = ":"), as.numeric),
         start_touch = 60 * map_dbl(split_start, ~ .x[1]) + map_dbl(split_start, ~ .x[2]),
         end_touch = 60 * map_dbl(split_end, ~ .x[1]) + map_dbl(split_end, ~ .x[2]),
         touch_duration = end_touch - start_touch) %>%
  select(-split_start, -split_end) %>%

  # merge with the dish-to-treat_num mappings
  left_join(blind_codes_full %>% select(-treatment), by = c("tray", "dish")) %>%  
  
  # merge with the treat_num-to-pheromone mappings
  left_join(blind_codes, by = "treat_num") %>%        
  
  # merge with the datasheet that lists how many bees were in each Petri dish (usually 5, occasionally 4)
    left_join(read_csv("data/metadata_for_each_dish_and_tray.csv", ) %>%
              select(tray, dish, number_bees), by = c("tray", "dish")) %>%
  
  # re-order the rows and columns for neatness
  select(hive, treatment, tray, dish, number_bees, 
         start_touch, end_touch, touch_duration) %>%
  mutate(treatment = factor(treatment, levels = treatment_levels)) %>%
  arrange(hive, treatment, tray, dish)
```


### Write a file containing the un-blinded data

The output shows the first 6 rows of the output file, `data/unblinded_behaviour_data.csv`.
```{r}
unblinded_data %>% write_csv("data/unblinded_behaviour_data.csv")
unblinded_data %>% head()
```


