---
title: "Pre-registered statistical analysis"
output: 
  workflowr::wflow_html:
    code_folding: hide 
editor_options:
  chunk_output_type: console
---

## Load packages and the behavioural data

```{r message=FALSE, warning=FALSE}
# However it was slightly tricky to install the showtext package. On Mac, I did this:
# installed 'homebrew' using Terminal: ruby -e "$(curl -fsSL https://raw.githubusercontent.com/Homebrew/install/master/install)" 
# installed 'libpng' using Terminal: brew install libpng
# installed 'showtext' in R using: devtools::install_github("yixuan/showtext")  
library(showtext)

library(tidyverse)
library(ggbeeswarm)
library(tidybayes)
library(brms)
library(gridExtra)
library(kableExtra)
library(bayestestR)
library(knitrhooks) # install with devtools::install_github("nathaneastwood/knitrhooks")
library(showtext)
library(ggrepel)
library(cowplot)

output_max_height() # a knitrhook option
options(stringsAsFactors = FALSE)

# set up nice font for figures
nice_font <- "Raleway"
font_add_google(name = nice_font, family = nice_font, regular.wt = 400, bold.wt = 700)
showtext_auto()

# Here are the treatments, ranked roughly from least to most like a queen bee
treatment_levels <-
  # two "controls"
  c("Solvent control", "10-HDA (worker control)",

    # 4 individual queen-type chemicals
    "HOB", "HVA", "9-HDA", "9-ODA",

    # 6 pairwise combinations of two of the queen-type chemicals
    "HOB and HVA",
    "9-HDA and HOB", "9-HDA and HVA",
    "9-ODA and HOB", "9-ODA and HVA", "9-ODA and 9-HDA")
levels_ampersand <- str_replace_all(treatment_levels, "and", "&")


# Load the behaviour data and rename the variables as in the pre-registration
# Also put the pheromone treatment levels in a biologically sensible order (not alphabetical)
behaviour_data <- read.csv("data/unblinded_behaviour_data.csv") %>%
  as_tibble() %>%
  rename(block = tray,
         hive = hive) %>%
  mutate(treatment = factor(treatment, levels = treatment_levels))

# Finally, count up the number of times the bees in each dish inspected the filter paper, 
# so that we now have 1 observation for each Petri dish (number of inspections in 30 minute-observation period)
data_by_petri_dish <- behaviour_data %>% 
  group_by(treatment, block, hive, dish) %>%
  summarise(n_inspections = length(touch_duration),
            duration_inspections = sum(touch_duration) + 1, # +1 is for the log10 analyses
            .groups = "drop") %>% 
  ungroup() %>%
  arrange(treatment, hive, block) 
```


## Plotting the raw data

These plots show the means $\pm$ SE (top) or the individual data points with boxplots for each group of bees (bottom). The left plots show the number of times bees inspected the pheromone lure in 30 minutes, while the right plots show the total duration the bees were inspecting the lure. 
```{r fig.height=10, fig.showtext=TRUE}
raw_to_plot <- data_by_petri_dish %>% 
  mutate(treatment = str_replace_all(treatment, "and", "&"),
         treatment = factor(treatment, levels_ampersand))


p1 <- raw_to_plot %>%
  group_by(treatment) %>%
  summarise(mean = mean(n_inspections),
            SE = sd(n_inspections) / sqrt(n()),
            .groups = "drop") %>%
  mutate(treatment = factor(treatment, rev(treatment))) %>%
  ggplot(aes(treatment, mean, fill = treatment)) + 
  geom_errorbar(aes(ymin = mean-SE, ymax = mean+SE), width = 0.2) + 
  geom_bar(stat="identity", colour = "black") + coord_flip() + 
  xlab("Treatment") +
  ylab("Mean \u00B1 SE number of inspections") +
    theme(legend.position = "none",
          text = element_text(family = nice_font))

p2 <- raw_to_plot %>%
  group_by(treatment) %>%
  summarise(mean = mean(duration_inspections),
            SE = sd(duration_inspections) / sqrt(n()),
            .groups = "drop") %>%
  mutate(treatment = factor(treatment, rev(treatment))) %>%
  ggplot(aes(treatment, mean, fill = treatment)) + 
  geom_errorbar(aes(ymin = mean-SE, ymax=mean+SE), width = 0.2) + 
  geom_bar(stat="identity", colour = "black") + coord_flip() + 
  xlab(NULL) +
  ylab("Mean \u00B1 SE total duration of inspections (s)") +
  theme(legend.position = "none",
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        text = element_text(family = nice_font))

p3 <- raw_to_plot %>%
    mutate(treatment = factor(treatment, rev(levels(treatment)))) %>%
    ggplot(aes(treatment, n_inspections, colour = treatment)) + 
    geom_beeswarm(alpha = .7) + 
    geom_boxplot(fill = NA, colour = "black", size = 0.3, outlier.shape = NA) +
    coord_flip() + 
    ylab("Number of inspections") + 
    xlab("Treatment") +
    theme(legend.position = "none",
        text = element_text(family = nice_font))

p4 <- raw_to_plot %>%
    mutate(treatment = factor(treatment, rev(levels(treatment)))) %>%
    ggplot(aes(treatment, duration_inspections, colour = treatment)) + 
    geom_beeswarm(alpha = .7) + 
    geom_boxplot(fill = NA, colour = "black", size = 0.3, outlier.shape = NA) +
    coord_flip() + 
    #scale_y_log10() + 
    ylab("Total duration of inspections") + 
    xlab(NULL) +
    theme(legend.position = "none",
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          text = element_text(family = nice_font))

plot(rbind(cbind(ggplotGrob(p1), ggplotGrob(p2), size = "last"),
           cbind(ggplotGrob(p3), ggplotGrob(p4), size = "last")))
```



## Analysis of the number of inspections

### Recap of the pre-registered plan for the analysis

In this section (i.e. `Analysis of the number of inspections`), we carry out the pre-planned analysis, focusing on the response variable that was mentioned in the pre-registration (represented in this R Markdown document by the variable `data_by_petri_dish$n_inspections`).

To recap, the pre-registered plan for this study can be found at [https://osf.io/ncf9z/](), and the relevant part is quoted here:

> _We will conduct two separate analyses, one for the behavioural data and one for the ovary dissection data. The analyses will use generalised linear mixed models (GLMM) be implemented using the R package brms, using one of the following two model formulas (in the syntax of brms): \p Model 1: `Response_variable ~ Pheromone_treatment + (1 | Block) + (1 | Hive)` &nbsp; &nbsp; or &nbsp; &nbsp;  Model 2: `Response_variable ~ Pheromone_treatment + (1 | Block) + (Pheromone_treatment | Hive)` \p Where `Pheromone_treatment` is a 12-level fixed factor. Model 1 fits hive as a random intercept, which constrains all the hives to show the same response to queen pheromone, while the latter allows for a variable response between hives by additionally including treatment as a random slope. We will use cross-validation to determine which of these models provides a better fit, and then use that in subsequent analyses. The behavioural data represent counts of events, and so will probably be analysed using a GLMM with Poisson errors (or perhaps zero-inflated Poisson or negative binomial – to be decided based on which one provides the best fit, according to posterior predictive checks)._


In the next section (`Analysis of inspection duration`), we use the same statistical methods to analyse the other response variable, namely the total duration that bees were inspecting the lure over the 30-minute observation period (measured in "bee seconds"; represented in this document by the variable `data_by_petri_dish$duration_inspections`). As the plot above suggests, the differences between treatments are larger for the `duration_inspections` response variable than for `n_inspections` though the results are qualitatively similar.


### Plot distribution of the response variable, `n_inspections`

The response variable does not look zero-inflated (as we speculated in the pre-registration), though the right tail seems longer than expected for a Poisson-distributed random variable. Therefore, it seems appropriate to select the negative binomial distribution, which has an additional free parameter for the variance, and so should provide a better fit to the data.

```{r}
ggplot(data_by_petri_dish, aes(n_inspections)) + 
  geom_histogram(bins = 50, colour = "grey20", fill = "#f69256") +
  xlab("Number of inspections")
```


### Run the pre-registered models in `brms`

Here, we run the models as stated in the pre-registration. 

```{r run_all_models}
if(!file.exists("output/pre_reg_model.rds")){ 
  
  priors <- c(prior(normal(0, 3), class = b))
  
  pre_reg_model <- brm(
    formula = n_inspections ~ treatment + (1 | block) + (1 | hive),
    family = "negbinomial",
    chains = 4, cores = 1, iter = 8000,
    control = list(adapt_delta = 0.9999, max_treedepth = 14),
    prior = priors,
    data = data_by_petri_dish)
  saveRDS(pre_reg_model, file = "output/pre_reg_model.rds")
  
  pre_reg_with_random_slope <- brm(
    formula = n_inspections ~  treatment + (1 | block) + (treatment | hive), 
    family = "negbinomial", 
    sample_prior = TRUE,
    chains = 4, cores = 1, iter = 8000,
    control = list(adapt_delta = 0.9999, max_treedepth = 14),
    prior = priors,
    data = data_by_petri_dish)
  
  model_weights_random_slope <- model_weights(pre_reg_model, pre_reg_with_random_slope, weights = "loo")
  saveRDS(model_weights_random_slope, "output/model_weights_random_slope.rds")

} else {
  pre_reg_model <- readRDS("output/pre_reg_model.rds")
  model_weights_random_slope <- readRDS("output/model_weights_random_slope.rds")
}
```


### Model results

#### The model without the random slope fits better

The model formula named "Model 1" in the pre-registration had a better fit than the one named Model 2; that is, there was no evidence for variance in the response to treatment between hives. The model weight of Model 1 was >99.999% (computed using "LOO", or leave-one-out cross validation), indicating strong support for Model 1 over Model 2.

```{r}
model_weights_random_slope 
```


#### Posterior predictive plots to verify model fit

We first perform a "posterior predictive check" on the model. The thick line shows the distribution of the real data, and the 10 thin blue lines show the distribution of fitted values for 10 random draws from the posterior. The fitted values follow the original data quite well, which is a necessary condition for a model to produce reliable inferences. 

```{r message=FALSE, warning=FALSE}
pp_check(pre_reg_model, nsamples = 10) + 
  labs(y = "Density", x = "Number of inspections")
```

#### Raw output provided by `brms` 

Here is the complete output from the `summary()` method for `brms`.

```{r output_max_height = "300px"}
summary(pre_reg_model)
```


#### Table of the fixed effects estimates

Table SXXX: Treatment effects on the number of inspections of the pheromone lure observed in 30 minutes. The table shows the fixed effects parameter estimates from a Bayesian mixed model with negative binomial errors, and hive and experimental block as random effects. Columns 2-5 show the median, error, and 95% credible intervals of the posterior distribution, while the p column shows 1 minus the "probability of direction" (i.e. the probability that the true effect size has the same sign as the estimated effect size). 

```{r}
pvalues <- as.data.frame(p_direction(pre_reg_model)) %>% 
  mutate(Parameter = str_remove_all(Parameter, "b_"),
         Parameter = str_replace_all(Parameter, "[.]", ":"),
         p = 1- pd)  %>% select(Parameter, p) %>% distinct()

fixed_effects <- fixef(pre_reg_model) %>% 
  as.data.frame() %>%
  rownames_to_column("Parameter") %>%
  mutate(old_names = Parameter) %>%
  left_join(pvalues, by = "Parameter") %>%
  mutate(` ` = ifelse(p < 0.05, "\\*", ""),
         ` ` = replace(` `, p > 0.05 & p < 0.1, "~"),
         ` ` = replace(` `, p < 0.01, "**"), 
         ` ` = replace(` `, p < 0.001, "***"),
         Parameter = str_replace_all(Parameter, "Pheromone_treatment", ""),
         Parameter = str_replace_all(Parameter, "M", "-"),
         Parameter = str_replace_all(Parameter, "and", " and "),
         Parameter = str_replace_all(Parameter, "workercontrol", " (worker control)"),
         Parameter = str_replace_all(Parameter, "treatment", "Treatment: ")) %>%
  mutate_at(vars(-Parameter, - ` `, - old_names), ~ round(.x, 3)) 

fixed_effects %>% select(-old_names) %>%
  mutate(Parameter = str_replace_all(Parameter, "and", "&")) %>% 
  kable() %>% kable_styling(full_width = FALSE)
```



### Plotting the parameter estimates from the model

```{r fig.height=6, fig.showtext = TRUE}
plot_model <- function(model){
  posterior_samples(model) %>% 
    as_tibble() %>%
    select(contains("b_"), -contains("Intercept")) %>%
    gather() %>% 
    mutate(key = str_remove_all(key, "b_")) %>%
    left_join(fixed_effects %>% select(Parameter, old_names), by = c("key" = "old_names")) %>%
    mutate(Parameter = str_replace_all(Parameter, "Treatment: ", "")) %>% 
    mutate(Parameter = str_replace_all(Parameter, "and", "&")) %>% 
    mutate(Parameter = factor(Parameter, rev(levels_ampersand))) %>%
    filter(!is.na(Parameter)) %>% 
    ggplot(aes(value, Parameter, fill = Parameter)) +
    geom_vline(xintercept = 0, linetype = 2) + 
    stat_halfeyeh(alpha = 0.8) +
    scale_fill_viridis_d() +
    theme_bw() +
    theme(legend.position = "none",
        text = element_text(family = nice_font)) + 
    ylab("Pheromone treatment") +
    xlab("Effect on number of inspections\n(relative to the solvent-only control)")
}

pre_reg_model %>% plot_model()
```
<br></br>
**Figure S1**: The figure shows the posterior distribution for each chemical's effect size, from the pre-registered model shown in Table SXX. The solvent-only control was used as the reference level, meaning that positive effect sizes indicate that the focal chemical received more inspections from worker bees than the solvent-only control, and negative effect sizes mean it received fewer inspections. Note that there is some evidence that the true effect size is positive for the four treatments containing 9-ODA, though there is no evidence that pairs of chemicals had synergistic effects. 


### Pairwise comparisons of means (planned contrasts) {.tabset}

We also wrote the following in the pre-registered plan for the analysis:

> Firstly, we will calculate pairwise differences in means between all the 12 treatments, similar to post hoc testing in the frequentist framework. For example, we might find that the mean number of contacts with the pheromone lure was significantly higher in the 9-ODA treatment relative to the solvent control 

Here, we calculate the posterior estimates for the mean number of inspections of the pheromone lure for each of the 12 treatments, and then find the _difference_ in means between various pairs of treatments. For example, we compare each of the 11 treatments to the solvent-only control, and compare each of the two-component mixtures to the individual chemicals they contain. In the graph below, the y-axis includes a minus sign (`−`) to illustrate the direction of the comparison, e.g. positive values for the first variable (`9-ODA & HOB − HOB`) indicate the mixture of 9-ODA & HOB had a higher number of inspections than HOB alone. 

#### Figure

```{r fig.showtext=TRUE, fig.height=7}
new <- data_by_petri_dish %>% 
  select(treatment) %>% distinct() %>% 
  arrange(treatment) %>% 
  mutate(para = paste("V", 1:n(), sep = ""))

contrasts_n_inspections <- as.data.frame(fitted(pre_reg_model, newdata = new, 
                     re_formula = NA, summary = FALSE)) %>% 
  mutate(draw = 1:n()) %>% 
  as_tibble() %>% 
  gather(para, n_inspections, -draw) %>% 
  left_join(new, by = "para") %>% 
  select(draw, treatment, n_inspections) %>% 
  spread(treatment, n_inspections) %>% 
  mutate(
    `HOB & HVA − HOB` = `HOB and HVA` - HOB,
    `HOB & HVA − HVA` = `HOB and HVA` - HVA,
    
    `9-HDA & HOB − 9-HDA` = `9-HDA and HOB` - `9-HDA`,
    `9-HDA & HOB − HOB` = `9-HDA and HOB` - HOB,
    
    `9-HDA & HVA − 9-HDA` = `9-HDA and HVA` - `9-HDA`,
    `9-HDA & HVA − HVA` = `9-HDA and HVA` - HVA,
    
    `9-ODA & HOB − 9-ODA` = `9-ODA and HOB` - `9-ODA`,
    `9-ODA & HOB − HOB` = `9-ODA and HOB` - HOB,
    
    `9-ODA & HVA − 9-ODA` = `9-ODA and HVA` - `9-ODA`,
    `9-ODA & HVA − HVA` = `9-ODA and HVA` - HVA,
    
    `9-ODA & 9-HDA − 9-ODA` = `9-ODA and 9-HDA` - `9-ODA`,
    `9-ODA & 9-HDA − 9-HDA` = `9-ODA and 9-HDA` - `9-HDA`,
    
    `10-HDA (worker control) − solvent` = `10-HDA (worker control)` - `Solvent control`,
    `HOB − solvent` = HOB - `Solvent control`,
    `HVA − solvent` = HVA - `Solvent control`,
    `9-HDA − solvent` = `9-HDA` - `Solvent control`,
    `9-ODA − solvent` = `9-ODA` - `Solvent control`,
    `HOB & HVA − solvent` = `HOB and HVA` - `Solvent control`,
    `9-HDA & HOB − solvent` = `9-HDA and HOB` - `Solvent control`,
    `9-HDA & HVA − solvent` = `9-HDA and HVA` - `Solvent control`,
    `9-ODA & HOB − solvent` = `9-ODA and HOB` - `Solvent control`,
    `9-ODA & HVA − solvent` = `9-ODA and HVA` - `Solvent control`,
    `9-ODA & 9-HDA − solvent` = `9-ODA and 9-HDA` - `Solvent control`
    ) %>% select(draw, contains("−")) 

get_p <- function(x) 1 - as.numeric(p_direction(x))

contrast_table_n_inspections <- left_join(
  contrasts_n_inspections[,-1] %>% 
    summarise_all(~ list(as.data.frame(posterior_summary(.x)))) %>% 
    gather(Contrast, value) %>% unnest(value),
  contrasts_n_inspections[,-1] %>% 
    summarise_all(~ get_p(.x)) %>% 
    gather(Contrast, p) %>% unnest(p), by = "Contrast") %>% 
  mutate(` ` = ifelse(p < 0.05, "\\*", ""),
         ` ` = replace(` `, p > 0.05 & p < 0.1, "~"),
         ` ` = replace(` `, p < 0.01, "**"), 
         ` ` = replace(` `, p < 0.001, "***")) %>% 
  arrange(-Estimate)

contrasts_n_inspections %>% 
  gather(contrast, difference, -draw) %>% 
  mutate(contrast = factor(contrast, rev(contrast_table_n_inspections$Contrast))) %>% 
  ggplot(aes(difference, contrast, fill = contrast)) +
  stat_eyeh() + 
  geom_vline(xintercept = 0, linetype = 2) +
  coord_cartesian(xlim = c(-30, 40)) +
  theme(legend.position = "none", 
        text = element_text(family = nice_font)) + 
  xlab("Posterior difference in means")
```


#### Table of contrasts

The table shows summary statistics about the posterior distribution of the contrasts shown in the previous figure. 

```{r}
contrast_table_n_inspections %>% 
  kable() %>% kable_styling(full_width = FALSE)
```


### Synergy score

We also wrote the following in the pre-registered plan for the analysis:

> Secondly, we will test for non-additive effects such as synergy among the pheromone components, by evaluating the following null hypothesis: $d_{1,2} = d_1 + d_2$, where $d_1$ is the estimated effect of pheromone 1 on the response variable, $d_2$ is the estimated effect of pheromone 2, and $d_{1,2}$ is the effect of the mixture of both pheromones. The effect sizes will each be expressed as the posterior difference in means relative to the control. For example, if both individual pheromones had a positive effect on the response variable individually, and the pair of pheromones had an effect size greater than the sum of their individual effects, we would call that pair of pheromones synergistic. If the effect of the pair was less than the sum of the two individual effects, the pheromones could be said to interfere with one another.

We here calculate the posterior estimate of the "synergy score", $d_{1,2} - d_1 + d_2$. When there is good evidence for the synergy, the posterior distribution should not overlap zero, which is not the case for any of the two-component mixtures that we examined. 

```{r fig.showtext=TRUE, warning=FALSE}
synergy_plot <- function(df, lims){
  df %>% 
    select(contains("solvent")) %>% 
    rename_all(~ str_remove_all(.x, " − solvent")) %>% 
    rename_all(~ str_remove_all(.x, "treatment")) %>%
    rename_all(~ str_remove_all(.x, "M")) %>%
    mutate(sum_HOB_HVA = HOB + HVA,
           sum_9HDA_HOB = `9-HDA` + HOB,
           sum_9HDA_HVA = `9-HDA` + HVA,
           sum_9ODA_HOB = `9-ODA` + HOB,
           sum_9ODA_HVA = `9-ODA` + HVA,
           sum_9ODA_9HDA = `9-ODA` + `9-HDA`) %>% 
    mutate(syn_HOB_HVA   = `HOB & HVA` - sum_HOB_HVA,
           syn_9HDA_HOB  = `9-HDA & HOB` - sum_9HDA_HOB,
           syn_9HDA_HVA  = `9-HDA & HVA` - sum_9HDA_HVA,
           syn_9ODA_HOB  = `9-ODA & HOB` - sum_9ODA_HOB,
           syn_9ODA_HVA  = `9-ODA & HVA` - sum_9ODA_HVA,
           syn_9ODA_9HDA = `9-ODA & 9-HDA` - sum_9ODA_9HDA) %>% 
    select(starts_with("syn")) %>% 
    rename_all(~ str_remove_all(.x, "syn_")) %>% 
    rename_all(~ str_replace_all(.x, "_", " & ")) %>% 
    rename_all(~ str_replace_all(.x, "9", "9-")) %>% 
    gather() %>% 
    ggplot(aes(value, key, fill = key)) + 
    geom_vline(xintercept = 0, linetype = 2) +
    stat_halfeyeh(alpha = 0.8) +
    scale_fill_viridis_d(option = "B") +  
    coord_cartesian(xlim = lims) + ylab("Pheromone pair") + xlab("Synergy score") +
    theme_bw() + 
    theme(legend.position = "none",
        text = element_text(family = nice_font))
}

contrasts_n_inspections %>% synergy_plot(c(-50, 50))
```





## Analysis of inspection duration

### Plot distribution of the response variable, `duration_inspections`

The response variable is highly non-Normal, though a log transformation produces an approximately Normal distribution. We therefore chose to analyse these data with the `lognormal` family in `brms`, which is designed for variables for which a log transformation makes the distribution approximately Normal. We also tested a model using the `gamma` family, but this model provided a worse fit than the `lognormal` model as ranked by leave-one-out cross validation (not shown).

```{r}
grid.arrange(
  ggplot(data_by_petri_dish, aes(duration_inspections)) + 
    geom_histogram(bins = 50, colour = "grey20", fill = "#f69256") +
    xlab("Total duration of inspections"),
  ggplot(data_by_petri_dish, aes(duration_inspections)) + 
    geom_histogram(bins = 50, colour = "grey20", fill = "#f69256") +
    scale_x_log10() + 
    xlab("Total duration of inspections (log10 scale)")
)
```

### Run the model (lognormal GLMM)

The predictors and priors in the Bayesian GLMM are the same as before, with one one difference: the predictor `hive` has been treated as a fixed effect (not random), because the model did not sample properly when `hive` was modeled as a random effect. Random effects are sometimes difficult to fit when there are few levels (here, there are only 3 hives), and the usual solution is to use a fixed effect. 

```{r}
if(!file.exists("output/pre_reg_model.rds")){ 
  duration_model <- brm(
    formula = duration_inspections ~ treatment + (1 | block) + hive,
    family = "lognormal", 
    chains = 4, cores = 1, iter = 8000,
    control = list(adapt_delta = 0.9, max_treedepth = 14),
    prior = priors,
    data = data_by_petri_dish)
  
  saveRDS(duration_model, file = "output/duration_model.rds")
}
duration_model <- readRDS("output/duration_model.rds")
```



### Model results

#### Posterior predictive plots to verify model fit

We first perform a "posterior predictive check" on the models. The thick line shows the distribution of the real data, and the 10 thin blue lines show the distribution of fitted values for 10 random draws from the posterior. The fitted values follow the original data quite well, which is a necessary condition for a model to produce reliable inferences. 

```{r message=FALSE, warning=FALSE}
pp_check(duration_model, nsamples = 10) + scale_x_log10() + 
  labs(y = "Density", x = "Total duration of inspections (s)")
```

Here is the complete output from the `summary()` method for the models fitted with `brms`. The `summary()` shows the random effects, which were omitted from the previous table.

#### Raw output provided by `brms`

Here is the complete output from the `summary()` method for the models fitted with `brms`.

```{r output_max_height = "300px"}
summary(duration_model)
```


#### Table of the fixed effects estimates

Table SXXX: Treatment effects on the total duration of inspections of the pheromone lure (in seconds) observed over 30 minutes. The table shows the fixed effects parameter estimates from a Bayesian mixed model with negative binomial errors, and hive and experimental block as random effects. Columns 2-5 show the median, error, and 95% credible intervals of the posterior distribution, while the p column shows 1 minus the "probability of direction" (i.e. the probability that the true effect size has the same sign as the estimated effect size). 

```{r}
pvalues <- as.data.frame(p_direction(duration_model)) %>% 
  mutate(Parameter = str_remove_all(Parameter, "b_"),
         Parameter = str_replace_all(Parameter, "[.]", ":"),
         p = 1- pd)  %>% select(Parameter, p) %>% distinct()

fixed_effects <- fixef(duration_model) %>% 
  as.data.frame() %>%
  rownames_to_column("Parameter") %>%
  mutate(old_names = Parameter) %>%
  left_join(pvalues, by = "Parameter") %>%
  mutate(` ` = ifelse(p < 0.05, "\\*", ""),
         ` ` = replace(` `, p > 0.05 & p < 0.1, "~"),
         ` ` = replace(` `, p < 0.01, "**"), 
         ` ` = replace(` `, p < 0.001, "***"),
         Parameter = str_replace_all(Parameter, "Pheromone_treatment", ""),
         Parameter = str_replace_all(Parameter, "M", "-"),
         Parameter = str_replace_all(Parameter, "and", " and "),
         Parameter = str_replace_all(Parameter, "workercontrol", " (worker control)"),
         Parameter = str_replace_all(Parameter, "treatment", "Treatment: ")) %>%
  mutate_at(vars(-Parameter, - ` `, - old_names), ~ round(.x, 3)) 

fixed_effects %>% select(-old_names) %>%
  mutate(Parameter = str_replace_all(Parameter, "and", "&")) %>% 
  kable() %>% kable_styling(full_width = FALSE)
```



#### Plotting the parameter estimates from the model
```{r fig.showtext=TRUE, fig.height=6, warning=FALSE}
duration_model %>% plot_model()
```


```{r fig.showtext=TRUE, echo = FALSE, warning=FALSE}
p1 <- pre_reg_model %>% plot_model() + xlab("Effect on number of inspections")
p2 <- (duration_model %>% plot_model()) + ylab(NULL) + xlab("Effect on total duration of inspections") +
    theme(axis.text.y = element_blank(),
          axis.ticks.y = element_blank())



ggsave(filename = "figures/fig1.pdf", 
       plot(cbind(ggplotGrob(p1), ggplotGrob(p2), size = "last")),
       height = 6, width = 7) 
```


### Pairwise comparisons of means (planned contrasts) {.tabset}

As before, we calculate contrasts comparing the mean of the response variable in several pairs of treatments (i.e. we compute contrasts).

#### Figure

```{r fig.showtext=TRUE, fig.height=7}
contrasts_duration <- as.data.frame(
  fitted(duration_model, 
         newdata = new %>% mutate(hive = "Skylab"), 
         re_formula = NA, summary = FALSE)) %>% 
  mutate(draw = 1:n()) %>% 
  as_tibble() %>% 
  gather(para, n_inspections, -draw) %>% 
  left_join(new, by = "para") %>% 
  select(draw, treatment, n_inspections) %>% 
  spread(treatment, n_inspections) %>% 
  mutate(
    `HOB & HVA − HOB` = `HOB and HVA` - HOB,
    `HOB & HVA − HVA` = `HOB and HVA` - HVA,
    
    `9-HDA & HOB − 9-HDA` = `9-HDA and HOB` - `9-HDA`,
    `9-HDA & HOB − HOB` = `9-HDA and HOB` - HOB,
    
    `9-HDA & HVA − 9-HDA` = `9-HDA and HVA` - `9-HDA`,
    `9-HDA & HVA − HVA` = `9-HDA and HVA` - HVA,
    
    `9-ODA & HOB − 9-ODA` = `9-ODA and HOB` - `9-ODA`,
    `9-ODA & HOB − HOB` = `9-ODA and HOB` - HOB,
    
    `9-ODA & HVA − 9-ODA` = `9-ODA and HVA` - `9-ODA`,
    `9-ODA & HVA − HVA` = `9-ODA and HVA` - HVA,
    
    `9-ODA & 9-HDA − 9-ODA` = `9-ODA and 9-HDA` - `9-ODA`,
    `9-ODA & 9-HDA − 9-HDA` = `9-ODA and 9-HDA` - `9-HDA`,
    
    `10-HDA (worker control) − solvent` = `10-HDA (worker control)` - `Solvent control`,
    `HOB − solvent` = HOB - `Solvent control`,
    `HVA − solvent` = HVA - `Solvent control`,
    `9-HDA − solvent` = `9-HDA` - `Solvent control`,
    `9-ODA − solvent` = `9-ODA` - `Solvent control`,
    `HOB & HVA − solvent` = `HOB and HVA` - `Solvent control`,
    `9-HDA & HOB − solvent` = `9-HDA and HOB` - `Solvent control`,
    `9-HDA & HVA − solvent` = `9-HDA and HVA` - `Solvent control`,
    `9-ODA & HOB − solvent` = `9-ODA and HOB` - `Solvent control`,
    `9-ODA & HVA − solvent` = `9-ODA and HVA` - `Solvent control`,
    `9-ODA & 9-HDA − solvent` = `9-ODA and 9-HDA` - `Solvent control`
    ) %>% select(draw, contains("−")) 


contrast_table_duration  <- left_join(
  contrasts_duration[,-1] %>% 
    summarise_all(~ list(as.data.frame(posterior_summary(.x)))) %>% 
    gather(Contrast, value) %>% unnest(value),
  contrasts_duration[,-1] %>% 
    summarise_all(~ get_p(.x)) %>% 
    gather(Contrast, p) %>% unnest(p), by = "Contrast") %>% 
  mutate(` ` = ifelse(p < 0.05, "\\*", ""),
         ` ` = replace(` `, p > 0.05 & p < 0.1, "~"),
         ` ` = replace(` `, p < 0.01, "**"), 
         ` ` = replace(` `, p < 0.001, "***")) %>% 
  arrange(-Estimate)

contrasts_duration %>% 
  gather(contrast, difference, -draw) %>% 
  mutate(contrast = factor(contrast, rev(contrast_table_duration$Contrast))) %>% 
  ggplot(aes(difference, contrast, fill = contrast)) +
  stat_eyeh() + 
  geom_vline(xintercept = 0, linetype = 2) +
  coord_cartesian(xlim = c(-400, 700)) +
  theme(legend.position = "none",
        text = element_text(family = nice_font)) + 
  xlab("Posterior difference in means")
```

#### Table of contrasts

The table shows summary statistics about the posterior distribution of the contrasts shown in the previous figure. 

```{r}
contrast_table_duration %>% 
  kable() %>% kable_styling(full_width = FALSE)
```


### Synergy score

We again calculate the posterior estimate of the "synergy score", $d_{1,2} - d_1 + d_2$. As before, the posterior distribution overlaps zero for every pair of chemicals, meaning that there is no strong evidence that any of the two-chemical mixtures have synergistic effects on the duration of inspections of the lure.

```{r}
contrasts_duration %>% synergy_plot(c(-500, 500))
```


```{r echo=FALSE}
p1 <- (contrasts_n_inspections %>% synergy_plot(c(-50, 50))) + 
  xlab("Synergy score\n(Number of inspections)")
p2 <- (contrasts_duration %>% synergy_plot(c(-500, 500))) + 
  ylab(NULL) + xlab("Synergy score\n(Duration of inspections)") +
  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank())

ggsave(filename = "figures/fig2.pdf", 
       plot(cbind(ggplotGrob(p1), ggplotGrob(p2), size = "last")),
       height = 5, width = 6) 
```




## Comparing our results to Slessor et al. 1988

### Plots to compare the results

```{r fig.showtext=TRUE, warning=FALSE, fig.width = 5, fig.height = 6}
# Transcribe the treatment group means and SE from the table in Slessor et al. 1988
slessor <- tibble(
  study = "slessor",
  mean = c(24.7, 17.1, 13.1, 6.1, 6.7, 3.4, 7.6, 9, 4.3, 3.5, 3.5, 3.9, 6.1, 4.7, 3.5, 2.9, 1.3),
  SE = c(3.3, 3.4, 2.3, 1.3, 1.7, .6, 1.1, 1.8, 1.1, 1, .6, .7, 1.3, .9, 1.3, .7, .4),
  n = 17,
  treatment = c("Queen extract", "9-ODA, 9-HDA, HOB, HVA", 
          "9-ODA, HOB, HVA", "9-HDA, HOB, HVA", 
          "9-ODA, 9-HDA, HOB", "9-ODA, 9-HDA, HVA",
          "HOB & HVA", "9-ODA & HOB", "9-ODA & HVA",
          "9-ODA & 9-HDA", "9-HDA & HOB", "9-HDA & HVA",
          "9-ODA", "HVA", "9-HDA", "HOB", "Solvent control")
) 

slessor_levels <- slessor %>%
  arrange(mean) %>% pull(treatment)

barplot_data <- slessor %>%
  arrange(mean) %>%
  mutate(study = " Slessor et al. 1988") %>%
  bind_rows(data_by_petri_dish %>%
              filter(treatment != "10-HDA (worker control)") %>%
              group_by(treatment) %>%
              summarise(mean = mean(duration_inspections),
                        SE = sd(duration_inspections) / sqrt(n()),
                        .groups = "drop") %>%
              mutate(study = "Present study", n = NA,
                     treatment = str_replace_all(as.character(treatment), "and", "&")) %>%
              select(study, mean, SE, n, treatment)) %>%
  filter(treatment %in% levels_ampersand) %>%
#  filter(study != "Our study") %>%
  mutate(treatment = factor(treatment, slessor_levels)) 

comparison_barplot <- barplot_data %>%
  ggplot(aes(treatment, mean, fill = treatment)) + 
  geom_errorbar(aes(ymin = mean-SE, ymax=mean+SE), width = 0.3) + 
  geom_bar(stat="identity", colour = "black") + coord_flip() +
  scale_fill_viridis_d(direction = -1) +
  theme(legend.position = "none",
        text = element_text(family = nice_font)) + 
  ylab("Mean + SE retinue response") + 
  xlab("Treatment") + 
  facet_wrap(~study, scales = "free_x") +
  theme_bw() +
  theme(legend.position = "none",
        text = element_text(family = nice_font), 
        strip.background = element_blank())

correlation_data <- slessor %>%
  select(treatment, mean, SE, study) %>%
  bind_rows(data_by_petri_dish %>%
              group_by(treatment) %>%
              summarise(mean = mean(duration_inspections),
                        SE = sd(duration_inspections) / sqrt(n()),
                        .groups = "drop") %>%
              mutate(study = "us",
                     treatment = str_replace_all(as.character(treatment), "and", "&"))) %>%
  filter(treatment %in% unique(barplot_data$treatment)) %>%
  group_by(study, treatment) %>%
  nest() %>%
  spread(study, data) %>%
  unnest(slessor) %>% rename(slessor_mean = mean, slessor_SE = SE) %>%
  unnest(us) %>% rename(our_mean = mean, our_SE = SE) %>% 
  mutate(treatment = factor(treatment, levels(barplot_data$treatment)))

comparison_scatter <- correlation_data %>%
  ggplot(aes(x = slessor_mean, y = our_mean)) + 
  stat_smooth(method = "lm", colour = "grey20", formula = "y ~ x", size = 0.7, aes(weight = our_SE)) +
  geom_errorbar(aes(ymin = our_mean - our_SE, ymax = our_mean + our_SE), size = 0.25, width = 0, colour = "grey20") + 
  geom_errorbarh(aes(xmin = slessor_mean - slessor_SE, xmax = slessor_mean + slessor_SE), size = 0.25, height = 0, colour = "grey20") + 
  geom_point(pch = 21, aes(fill =  treatment)) + 
  scale_fill_viridis_d(direction = -1) +
  geom_text_repel(aes(label = treatment), colour = "black", size = 3, family = nice_font) +
  ylab("Mean retinue response \u00B1 SE\n(present study)") + 
  xlab("Mean retinue response \u00B1 SE (Slessor et al. 1988)") +
  theme_bw() +
  theme(legend.position = "none",
        text = element_text(family = nice_font))

composite_plot <- plot_grid(comparison_barplot, comparison_scatter, nrow = 2, align = 'v', axis = 'l')

ggsave(filename = "figures/fig3.pdf", 
       composite_plot, width = 5, height = 6)

composite_plot
```

### Spearman correlation between the effect sizes
```{r warning=FALSE}
cor.test(correlation_data$our_mean, 
         correlation_data$slessor_mean, method = "spearman")
```
